cvx-flats

### 2020-05-18 neurips-20/cvx-flats-statements.tex
End of day check in; added lemma statements and reorganized proofs of props 1 and 3

%\raf{Issues with the definition:
%\begin{enumerate}
%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
%\end{enumerate}
%At this point I lost the thread. It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis? -- and the implication also seems backwards.}
\begin{definition}[Consistent: property]
	Let $\{f_m: \X \to \R\}$ be a sequence of hypothesis functions.
	A loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$ pair $(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a distance $\mu:\R \times \R \to \reals_+$ if, for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and 
	\begin{equation}
	\E_{(X,Y) \sim D} L(\psi \circ f_m(X), Y) \to \E_{(X,Y) \sim D} L( \gamma(D_X), Y) \implies \E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0~.~
	\end{equation}
	If $\mu$ has a set as input, define $\mu(S_1, S_2) = \inf_{s_1 \in S_1, s_2 \in S_2} \mu(s_1, s_2)$.
\end{definition}

@@

\jessie{Should this also be a lemma instead of a proposition?}
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a (continuous) loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later.}
\end{proposition}
\begin{proof}
	Let $\gamma$ be the property elicited by $\ell$.
	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$. 
	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.

@@

\begin{theorem}\label{thm:consistent-implies-indir-elic}
	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
\end{theorem}
\begin{proof}
If we are given a loss $\ell$, then we can string together Proposition~\ref{prop:consistent-implies-calibrated} and Lemma~\ref{lem:calib-implies-indir} to observe consistency $\implies$ calibration $\implies$ indirect elicitation.

\jessie{Need to redo this}
If we are just given the property $\gamma$ without a loss, assume that we have a sequence of measurable hypotheses $\{f_m\} \to f$ such that $\E_{(X,Y) \sim D} L(\psi \circ f_m(D_X), Y) \to \E_{(X,Y) \sim D} L(\gamma(D_X), Y)$.
We must then have $\E_X \mu(\gamma(D_X), \psi \circ f_m(X)) \to 0$ by consistency.
As in the proof of Proposition~\ref{prop:consistent-implies-calibrated}, this must be true for all $D_x$ for $x \in \X$, so we can abstract to distributions over $\simplex$.
Now, by consistency, we have the expected losses converging implies $\{\psi \circ f_m\}$ is converging toward the optimal hypothesis for all possible inputs $x \in \X$.

Let $\Gamma$ be the property directly elicited by $L$.
We have $\Gamma(D_x) = f(x)$ for all $x \in \X$, so we can see that the precedent being true implies $\mu(\psi \circ f_m(x), \gamma(p)) \to 0$ for all $p\in \simplex$.
As $\mu$ is a distance, $\mu(\psi \circ f(x), \Gamma(p)) = \mu(\psi \circ \Gamma(p), \gamma(p)) = 0$ for all $p \in \simplex$, which implies $\gamma = \psi \circ \Gamma$.
Therefore, $L$ must indirectly elicit the property $\gamma = \lim_{m \to \infty} \{\gamma_m\}$ via the link $\psi$.
\end{proof}

@@

\newpage
\appendix
\section{Omitted proofs}
\begin{proposition}
	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration of a property via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
	\jessie{eventually want iff}
\end{proposition}
\begin{proof}
	Let $\Gamma$ be the property elicited by $L$.
	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.

	Suppose there was a distribution $p \in \simplex$ and sequence $\{u_m\} \to u$ so that $\ell(\psi(u_m);p) \not \to \risk{\ell}(p)$ but $L(u_m;p) \to \risk{L}(p)$.
	We would then have $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.

	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
	\begin{align*}
	\ell(\psi(u);p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))
	\end{align*}
	for all $u \in \reals^d$.
	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.

	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
	\begin{align*}
	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p)\\
	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)~.~
	\end{align*}
	As $\lim_{m \to \infty} \ell(\psi(u_m);p) > \risk{\ell}(p)$, the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$ at $0^+$, we must then have $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = \zeta(0) = c > 0$.

%	Now, suppose $\zeta(0) = 0$, and take the sequence $\{u_m\} \to \Gamma(p)$ where $\psi(u_m) \neq \gamma(p)$ for all $m$.	
%	We have 
%	\begin{align*}
%	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
%	\lim_{m \to \infty}\ell(\psi(u_m); p) &\leq \risk{\ell}(p) +  \lim_{\epsilon \to 0^+} \zeta(\epsilon)\\
%%	\ell(\psi(\Gamma(p)); p) - \risk{\ell}(p)&\leq \zeta(\risk{L}(p) - L(\Gamma(p);p))\\
%%	\ell(\psi(\Gamma(p)); p) - \risk{\ell}(p)&\leq \zeta(0)\\
%%	\ell(\psi(\Gamma(p)); p) &\leq \zeta(0) + \ell(\gamma(p); p)\\
%%	\ell(\psi(\Gamma(p)); p) &\leq \ell(\gamma(p); p)~.~
%	\end{align*}
%	As $\ell(\psi(u_m); p)> \risk{\ell}(p)$ (since $\R$ is finite) for all $m$, we then observe that $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$.
%	However, since $\zeta(0) = 0$, we violate continuity of $\zeta$ at $0^+$.
\end{proof}

@@

>>>>

%\raf{Issues with the definition:
%\begin{enumerate}
%\item Good to clarify $d:\R\times\R\to\reals_+$ -- done
%\item We have two $d$'s so we'll need a new letter... -- changed to $\mu$
%\item $D_X$ is not defined, but I got it -- clarified it was the marginal distribution
%\item You can't take an expectation over $\R$ values (not necessarily a subset of a vector space) and want the expectation over $X$ on the outside
%\end{enumerate}
%At this point I lost the thread. It looks like you're missing the hypothesis function, and $\Gamma(D)$ doesn't seem to type check -- but perhaps $\Gamma(D)$ was meant to depend on $X$ and be the hypothesis? -- and the implication also seems backwards.}
\begin{definition}[Consistent: property]
	Suppose we are given a loss $L : \R \times \Y \to \reals$ and link $\psi : \R \to \R'$.
	$(L, \psi)$ is \emph{$\mu$-consistent with respect to a property} $\gamma: \simplex \toto \R'$ for a function $\mu^\gamma:\R' \times \simplex \to \reals_+$ with $\mu^\gamma(r,p) = 0 \iff r \in \gamma(p)$, if for all $D$ over $\X \times \Y$ with marginal distributions $D_x$, and sequences $\{f_m: \X \to \R\}$, 
	\begin{equation}
	\E_{D} L(f_m(X), Y) \to \inf_f \E_{D} L( f(X), Y) \implies \E_X \mu^\gamma(\psi \circ f_m(X), D_X) \to 0~.~
	\end{equation}

	We simply say the pair is consistent with respect to $\gamma$ if there is a distance $\mu^\gamma$ such that $(L,\psi)$ are $\mu$-consistent with respect to $\gamma$.
\end{definition}

@@

\jessie{Should this also be a lemma instead of a proposition?}
\begin{proposition}\label{prop:consistent-implies-calibrated}
	If a (continuous) loss and link $(L, \psi)$ are consistent with respect to a loss $\ell$, then they are calibrated with respect to $\ell$.
	\jessiet{Probably appendix later.}
\end{proposition}
\begin{proof}
	\jessie{Contrapositive.
	Not calibrated means there is a sequence $\{u_m\}$ such that $R_L(u_m; p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$ via Lemma~\ref{lem:calib-converging-regrets}.
	Take $D = D_x = p$ for some $x \in \X$, and any sequence of functions $\{f_m\} \to f$ with $f_m(x) = u_m$ for all $f_m$. 
	Now we have $\E_D L(f_m(X), Y) \to \inf_f \E_D L(f(X), Y)$, but $\E_D \ell(\psi(f(X)), Y) \not \to \inf_f \E_D \ell(\psi(f(X)), Y)$, and therefore $(L, \psi)$ is not calibrated with respect to $\ell$. 
}

	Let $\gamma$ be the property elicited by $\ell$.
	Suppose $(L,\psi)$ is not calibrated with respect to $\ell$; we will show they are not consistent with respect to $\ell$ either.
	$(L, \psi)$ not calibrated with respect to $\ell$ means that there is some distribution $p \in \simplex$ such that there is no function $\zeta : \reals_+ \to \reals_+$ with $\zeta(0) = 0$ and continuous at $0^+$ such that, for all $u \in \reals^d$, we have $\ell(\psi(u); p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))$. 
	In other words, for all $\zeta$ satisfying the assumptions, we have $\ell(\psi(u); p) - \risk{\ell}(p) > \zeta(L(u;p) - \risk{L}(p))$ for some $u \in \reals^d$.
	In particular, there must exist a sequence $\{u_m\}$ so that $L(u_m;p) \to \risk{L}(p)$.

@@

\begin{lemma}\label{lem:consistent-loss-implies-prop}
	If $(L, \psi)$ are consistent with respect to $\ell$, then they are consistent with respect to $\gamma := \prop{\ell}$.
\end{lemma}
\begin{proof}
	\jessie{TODO}
\end{proof}

\begin{theorem}\label{thm:consistent-implies-indir-elic}
	If a surrogate and link pair $(L, \psi)$ is consistent with respect to a property $\gamma$ or loss $\ell$ eliciting $\gamma$, then $L$ indirectly elicits $\gamma$.
\end{theorem}
\begin{proof}
As consistency with respect to $\ell$ implies consistency with respect to $\gamma := \prop{\ell}$ (Lemma~\ref{lem:consistent-loss-implies-prop}), it suffices to show the result for consistency with respect to a property $\gamma$.

We show the contrapositive; suppose $(L, \psi)$ is not consistent with respect to $\gamma$, and take $\Gamma := \prop{L}$.
Then there is a distribution $p \in \simplex$ so that $u \in \Gamma(p)$ but $\psi(u) \not \in \gamma(p)$.
Consider the constant sequence $\{u_m\} = u$ for all $m$.

We then consider a distribution $D = D_x = p$ for some $x \in \X$ and any sequence $\{f_m\}$ so that $f_m(x) = u_m$ for all $m$.
This yields $\E_D L(f_m(X), Y) \to \inf_f L(f(X),Y)$ since $u \in \Gamma(p)$.
However, we have $\mu(\psi(u_m), \gamma(p)) \not \to 0$ as $\mu(\psi(u), \gamma(p)) \neq 0$, since $\psi(u) \not \in \gamma(p)$ and the sequence is constant.
Hence, we do not have consistency.
\end{proof}

@@

\newpage
\appendix
\section{Omitted proofs}
\begin{enumerate}
	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
	\item [C] For all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{enumerate}

\begin{proposition}
	When $\R$ is finite and $L$ continuous in $\reals^d$, calibration of a property via Definition~\ref{def:calibrated-general} implies calibration via Definition~\ref{def:calibrated-finite}.
	\jessie{eventually want iff}
\end{proposition}
\begin{proof}
	\jessie{Contrapositive; not calibration by def~\ref{def:calibrated-finite} implies $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_u L(u; p)$.
	Thus there is a sequence $\{u_m\}$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.  Now we contradict $D$ and by Lemma~\ref{lem:calib-converging-regrets}, we have not calibrated by Def~\ref{def:calibrated-general}. }

	We prove the contrapositive; if $(L, \psi)$ is not calibrated with respect to $\ell$ by Definition~\ref{def:calibrated-finite}, then it is not calibrated via Definition~\ref{def:calibrated-general} either.

	Suppose there was a distribution $p \in \simplex$ so that $\inf_{u : \psi(u) \not \in \gamma(p)} L(u;p) = \inf_{u} L(u;p)$.
	There must then be a sequence $\{u_m\} \to u$ so that $\lim_{m \to \infty} \psi(u_m) \not \in \gamma(p)$ and $L(u_m; p) \to \risk{L}(p)$.

	This consequently implies $R_L(u_m;p) \to 0$ as $L(u_m; p) \to \risk{L}(p)$, but as $\ell(\psi(u_m); p) \not \to \risk{\ell}(p)$ (if it did converge, then we would have $\psi(u_m) \to r \in \gamma(p)$), so $R_\ell(\psi(u_m); p) \not \to 0$.
	Thus, by Lemma~\ref{lem:calib-converging-regrets}, we have no calibration via Definition~\ref{def:calibrated-general}.

%	We want to show that there is no $\zeta:\reals_+ \to \reals_+$ continuous at $0^+$ with $\zeta(0) = 0$ so that 
%	\begin{align*}
%	\ell(\psi(u);p) - \risk{\ell}(p) \leq \zeta(L(u;p) - \risk{L}(p))
%	\end{align*}
%	for all $u \in \reals^d$.
%	We show that if this bound is satisfied, one of the two conditions on $\zeta$ (continuity at $0^+$ and $\zeta(0) = 0$) must be violated.
%	
%	
%	First, suppose that $\zeta$ is continuous at $0^+$ and the bound is satisfied.
%	Then for the sequence $\{u_m\} \to \Gamma(p)$, we have 
%	\begin{align*}
%	\lim_{m \to \infty}\ell(\psi(u_m); p) - \risk{\ell}(p)&\leq \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p))\\
%%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{m \to \infty} \zeta(L(u_m; p) - \risk{L}(p)\\
%	\lim_{m \to \infty}\ell(\psi(u_m) ; p) &\leq \risk{\ell}(p) + \lim_{\epsilon \to 0^+} \zeta(\epsilon)~.~
%	\end{align*}
%	As $\lim_{m \to \infty} \ell(\psi(u_m);p) > \risk{\ell}(p)$, the last inequality can only happen if $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = c > 0$, and by continuity of $\zeta$ at $0^+$, we must then have $\lim_{\epsilon \to 0^+} \zeta(\epsilon) = \zeta(0) = c > 0$.

\end{proof}

@@

\begin{lemma}\label{lem:calib-converging-regrets}
	A surrogate and link $(L,\psi)$ are calibrated (via definition~\ref{def:calibrated-general}) with respect to $\ell$ if and only if, for all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{lemma}
\begin{proof}
	$\implies$ Take a sequence $\{u_m\}$ so that $R_L(u_m;p) \to 0$.
	Since $\zeta(0) = 0$ and $\zeta$ is continuous at $0$, $\zeta(R_L(u_m;p)) \to 0$ by calibration.
	As regret is nonnegative, we then have $R_\ell(\psi(u_m); p) \to 0$

	$\impliedby$ \jessie{zhang 04 corollary}
\end{proof}
